Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
future work and conclusion self-notes.

\section{Future Work} 
{\color {red}
\noindent {\bfseries Changing the Current Interface} merge, push.

@@

\section{Conclusion}

>>>>

\section{Future Work} 
{\color {red}
Wait to fill this section out until we have finished analyzing the data from the quantitative
user study experiment. A lot of the future work can be in reference to this. Or, we can even
talk about what is in the discussion section. ... OR, maybe this section isn't even necessary.\\

\noindent {\bfseries Changing the Current Interface} merge, push. \\

@@

\section{Conclusion} 
{\color {red} I am a fan of not having long, rambling conclusions. I leave
that for the discussion section. This section is more of a courtesy to the 
people who read the abstract, look at the figures, and then read the 
conclusion. Think of something to tell those people here. Something along
the lines of a tl;dr summary of the paper.}
